### 2023-07-08 Article_PySF.tex
rev(myzhu) Revised the manuscript, and made a draft of the response.

{\bf \noindent PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} PyStructureFactor \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} \url{https://github.com/TheStarAlight/PyStructureFactor} \\
{\em Code Ocean capsule:} (to be added by Technical Editor) \\
{\em Licensing provisions:} Apache-2.0 \\
{\em Programming language:} Python 3                                  \\
{\em Supplementary material:}                                 \\
{\em Nature of problem:} The structure factor of a molecule in intense laser fields determines its orientation-dependent tunneling ionization rate, which is crucial for the studies of ultrafast molecular dynamics and its control. However, the strong-field community lacks an open-source code to calculate the molecular structure factor, and can only resort to known results of a few molecules. \\
{\em Solution method:} We develope the \texttt{PyStructureFactor} program with the structure factor of arbitrary molecules calculated using the weak-field asymptotic theory in the integral representation. The underlying electronic structure necessary for the calculation is obtained using the \texttt{PySCF} quantum chemistry package. \\
{\em Restrictions on the Accuracy:} The accuracy of the molecular structure factor calculated by \texttt{PyStructureFactor} is restricted by the level of precision of the electronic structure information extracted from the \texttt{PySCF} package. \\
\cyan{{\em Running time:} The running time depends on the size of the molecule and the basis set of the SCF calculation and other parameters passed to the program. The example in Fig.~\ref{fig:code_example} took 1.2 sec. on an AMD Ryzen 9 7950X CPU on the WSL Ubuntu 22.04 LTS.}
\end{small}

@@

                                      which controls the number of radial and angular grids, ranging from 0 to 9.

>>>>

{\bf \noindent PROGRAM SUMMARY} \\
\begin{small}
\noindent
{\em Program Title:} PyStructureFactor \\
{\em CPC Library link to program files:} (to be added by Technical Editor) \\
{\em Developer's repository link:} \url{https://github.com/TheStarAlight/PyStructureFactor} \\
{\em Code Ocean capsule:} (to be added by Technical Editor) \\
{\em Licensing provisions:} Apache-2.0 \\
{\em Programming language:} Python 3                                  \\
{\em Supplementary material:}                                 \\
{\em Nature of problem:} The structure factor of a molecule in intense laser fields determines its orientation-dependent tunneling ionization rate, which is crucial for the studies of ultrafast molecular dynamics and its control. However, the strong-field community lacks an open-source code to calculate the molecular structure factor, and can only resort to known results of a few molecules. \\
{\em Solution method:} We develope the \texttt{PyStructureFactor} program with the structure factor of arbitrary molecules calculated using the weak-field asymptotic theory in the integral representation. The underlying electronic structure necessary for the calculation is obtained using the \texttt{PySCF} quantum chemistry package. \\
{\em Restrictions on the Accuracy:} The accuracy of the molecular structure factor calculated by \texttt{PyStructureFactor} is restricted by the level of precision of the electronic structure information extracted from the \texttt{PySCF} package. \\
\cyan{{\em Running time:} The running time depends on the size of the molecule and the basis set of the SCF calculation and other parameters passed to the program. The example in Fig.~\ref{fig:code_example} took 1.2 sec. to finish on an AMD Ryzen 9 7950X CPU on the WSL Ubuntu 22.04 LTS.}
\end{small}

@@

                                      which controls the number of radial and angular grids \cyan{around each atom in the evaluation of the integration},
                                      ranging from 0 to 9.
